\addcontentsline{toc}{chapter}{\large Resources}

\section{Learn to Code}
\begin{enumerate}
    \item Harvard's CS50 Course
    \item \href{https://www.hackreactor.com/}{Hack Reactor} - "The most advanced coding bootcamp. Think like a software engineer."
    
    \item \href{https://www.geeksforgeeks.org/}{Geeks for Geeks} - Highly useful for not only learning to code various languages, but also for acing interview questions.
    
    \item \href{https://www.codecademy.com}{Code Academy} - A free coding website with courses for plenty of languages.
    
    \item \href{https://www.freecodecamp.org/}{Free Code Camp} - A completely free non-profit code camp that has several large scale projects that help you fill your portfolio.
    \item \href{https://github.com/getify/You-Dont-Know-JS}{You Don't Know JS} - Kyle Simpson's phenomenal book on learning and mastering JS.
    \item \href{https://devdocs.io/}{Dev Docs} a great place to find documentation for all sorts of things. Compiled into one website for your convenience.
\end{enumerate}


\section{Coding Interview Prep}
\begin{enumerate}
    \item \href{https://www.interviewcake.com/upgrade}{Interview Cake}
    \item \href{https://www.hiredintech.com/classrooms/system-design/lesson/60}{Hired in Tech}
\end{enumerate}

\section{Advice and Application}
\begin{enumerate}
    \item \href{https://www.freecodecamp.org/news/5-key-learnings-from-the-post-bootcamp-job-search-9a07468d2331/}{A blog post} about post boot camp job search
    
    \item \href{https://github.com/j-delaney/easy-application}{A list of companies} that are easy to apply to.
    
    \item \href{https://www.reddit.com/r/cscareerquestions/comments/1jov24/heres_how_to_prepare_for_tech_interviews/}{A reddit post} outlining steps for preparing for a tech interview. Useful for junior developers and people who haven't had an interview in a while
    
    \item \href{https://github.com/h5bp/Front-end-Developer-Interview-Questions}{Front End Developer Interview Questions}
    
    \item \href{https://leetcode.com/}{Leetcode} - A resource for algorithm and data structure questions
    
    \item \href{https://www.crackingthecodinginterview.com/}{Cracking the Coding Interview Book} - The go-to book for technical interview prep. Coderust 2.0 is an alternative resource if you're avoiding CTCI.
\end{enumerate}